---
title: "Meta-Analysis on Postoperative Atelectasis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{atelectasis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library, results="hide", message=FALSE}
library(metafor)
```


## Input data
```{r atelectasis}
dat.atelectasis <- escalc(measure="RR",
              ai=c( 3,  2,  4,  1,  0),
              bi=c(15, 33, 40, 44, 15),
              ci=c( 4,  6,  6,  2,  1),
              di=c(15, 29, 36, 43, 14),
              slab=c("Boules et al, 2011",
                     "Mahmoud et al, 2017",
                     "Li et al (Standard), 2020",
                     "Li et al (OLA), 2020",
                     "Ammar et al, 2021")
              )
```


## Primary analysis: Paul-Mandel without Hartung-Knapp-Sidik-Jonkman (HKSJ) modification 
```{r PM, fig.height=4, fig.width=7}
pm.atelectasis <- rma(yi, vi, data=dat.atelectasis, method="PM") 
forest(pm.atelectasis,
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```
These results agree with the paper (Fig 2, bottom).

## Sensitivity analysis
### Sensitivity analysis 1: FE model

```{r FE, fig.height=4, fig.width=7}
fe.atelectasis <- rma(yi, vi, data=dat.atelectasis, method="FE") 
forest(fe.atelectasis, 
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```

Note: The standard RE model without HKSJ modification is identical (not shown):
```{r RE, fig.height=4, fig.width=7}
re.atelectasis <- rma(yi, vi, data=dat.atelectasis, method="REML") 
```



### Sensitivity analysis 2: Paule-Mandel with HKSJ modification 
```{r PMHK, fig.height=4, fig.width=7}
pmhk.atelectasis <- rma(yi, vi, data=dat.atelectasis, method="PM", test="knha") 
forest(pmhk.atelectasis,
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```


### Sensitivity analysis 3: Odds ratios (Paule-Mandel without HKSJ modification)
```{r OR}
dat.atelectasis.OR <- escalc(measure="OR",
              ai=c(3, 2, 1, 1, 0),
              bi=c(15, 33, 43, 44, 15),
              ci=c(4, 6, 4, 2, 1),
              di=c(15, 29, 38, 43, 14),
              slab=c("Boules et al, 2011",
                     "Mahmoud et al, 2017",
                     "Li et al (Standard), 2020",
                     "Li et al (OLA), 2020",
                     "Ammar et al, 2021")
              )
```

```{r "PM - OR", fig.height=4, fig.width=7}

pm.OR.atelectasis <- rma(yi, vi, data=dat.atelectasis.OR, method="PM") 
forest(pm.OR.atelectasis,
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```

Results are similar to primary analysis results.



### Sensitivity analysis 4: leave-one-out analysis
### Atelectasis
```{r leave one out atel, fig.height=4, fig.width=7}
leave1.atel <- leave1out(pm.atelectasis)
forest.default(x=leave1.atel$estimate, ci.lb=leave1.atel$ci.lb, ci.ub=leave1.atel$ci.ub,
               slab=paste("Omitting ", leave1.atel$slab, sep=""),atransf=exp,
               at=log(c(0.15, 0.25, exp(pm.atelectasis$b), 1, 4)), xlim=log(c(0.01, 4.5)),
               refline=pm.atelectasis$b
              )
lines(x=log(c(1, 1)), y=c(0, 6))
```

Results are almost identical to results in paper (difference of 0.01 in the upper confidence interval for Mahmoud et al.).

### Funnel plot
```{r funnel, fig.height=4, fig.width=6}
funnel(pm.atelectasis, main="Standard Error")
regtest(pm.atelectasis)
```

