---
title: "Meta-Analysis on Postoperative Pneumonia"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library, results="hide", message=FALSE}
library(metafor)
```


## Input data
```{r pneumonia }
dat <- escalc(measure="RR",
              ai=c(3,   5,  2,  0,  1),
              bi=c(32, 39, 43, 15, 24),
              ci=c(6,   7,  4,  1,  2),
              di=c(29, 35, 41, 14, 23),
              slab=c("Mahmoud et al, 2017",
                     "Li et al (Standard), 2020",
                     "Li et al (OLA), 2020",
                     "Ammar et al, 2021",
                     "Yao et al, 2020"))
```

## Primary analysis: Paul-Mandel without Hartung-Knapp-Sidik-Jonkman (HKSJ) modification 
```{r PM, fig.height=4, fig.width=7}
pm <- rma(yi, vi, data=dat, method="PM") 
forest(pm,
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```
These results agree with the paper (Fig 2, top).

## Sensitivity analysis 1: FE model

```{r FE, fig.height=4, fig.width=7}
fe <- rma(yi, vi, data=dat, method="FE") 
forest(fe, 
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```

Note: The standard RE model without HKSJ modification is identical (not shown):
```{r RE, fig.height=4, fig.width=7}
re <- rma(yi, vi, data=dat, method="REML") 
```



## Sensitivity analysis 2: Paule-Mandel with HKSJ modification 
```{r PMHK, fig.height=4, fig.width=7}
pmhk <- rma(yi, vi, data=dat, method="PM", test="knha") 
forest(pmhk,
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```


## Sensitivity analysis 3: Odds ratios (Paule-Mandel without HKSJ modification)
```{r OR}
dat.OR <- escalc(measure="OR",
              ai=c(3,   5,  2,  0,  1),
              bi=c(32, 39, 43, 15, 24),
              ci=c( 6,  7,  4,  1,  2),
              di=c(29, 35, 41, 14, 23),
              slab=c("Mahmoud et al, 2017",
                     "Li et al (Standard), 2020",
                     "Li et al (OLA), 2020",
                     "Ammar et al, 2021",
                     "Yao et al, 2020"))
```

Results are similar:

```{r "PM - OR", fig.height=4, fig.width=7}
pm.OR <- rma(yi, vi, data=dat.OR, method="PM") 
forest(pm.OR,
       atransf=exp,
       at=log(c(0.01, 0.1, 0.5, 1, 4, 10)))
```

