---
title: "Secondary outcomes"
resource_files:
    - ../data
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{second-outcomes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



```{r library, include=FALSE}
library(metafor)
library(xtable)
```

```{r load, echo=FALSE}
initial.data <- read.csv(file="../data/secondary-outcomes.csv")
dat <- escalc(measure="MD", data=initial.data, m1i=m1i, sd1i=sd1i, n1i=n1i, m2i=m2i, sd2i=sd2i, n2i=n2i, slab=study)
```

## Create models
```{r models, echo=TRUE}
# Fig 2: Respiratory compliance (Cdyn)
cdyn.olv <- rma(yi, vi, data=dat, subset = (outcome1=="Cdyn" & time=="OLV"), method="PM")

# Fig 3: Plateau pressure (Plat)
plat.tlv <- rma(yi, vi, data=dat, subset = (outcome1=="Plat" & time=="TLV"), method="PM")
plat.olv <- rma(yi, vi, data=dat, subset = (outcome1=="Plat" & time=="OLV"), method="PM")

# Fig 4: Peak inspiratory pressure (Peak)
peak.tlv <- rma(yi, vi, data=dat, subset = (outcome1=="Peak" & time=="TLV"), method="PM")
peak.olv <- rma(yi, vi, data=dat, subset = (outcome1=="Peak" & time=="OLV"), method="PM")

# Fig 5: Arterial oxygen pressure (pO2)
po2.tlv <- rma(yi, vi, data=dat, subset = (outcome1=="pO2" & time=="TLV"), method="PM")
# po2.olv <- rma(yi, vi, data=dat, subset = (outcome1=="pO2" & time=="OLV"), method="PM")
# Error when using default options. Fix:
po2.olv <- rma(yi, vi, data=dat, subset = outcome1=="pO2" & time=="OLV", method="PM", control=list(tau2.max=1000))
```


## Collated results
```{r collate results, echo=FALSE, results="asis"}
est.ci <- function(mod){
  est.with.ci <- paste(round(mod$b, 2), " (", round(mod$ci.lb, 2), ", ", round(mod$ci.ub, 2), ")", sep="")
  est.with.ci
}
olv.results <- c(est.ci(cdyn.olv), est.ci(plat.olv), est.ci(peak.olv), est.ci(po2.olv))
tlv.results <- c("---", est.ci(plat.tlv), est.ci(peak.tlv), est.ci(po2.tlv))
second.results <- data.frame(OLV=olv.results,
                             TLV=tlv.results)
rownames(second.results) <- c("Cdyn", "Plateau", "Peak", "pO2")
results.tab <- xtable(second.results, align="rrr")
print(results.tab, type="html")
```

Evidence of effect in all secondary outcomes except Plateau+TLV. These effects persist when the HKSJ modification is used, with the exception of Plateau+OLV.


## Notes on secondary outcome figures in draft
* Figure 3 in paper has different headings compared to Figs 4 and 5.
* Fig 4 has TLV first, while Figs 3 and 5 have OLV first.
* TLV and OLV data have been mixed up in the document (assuming the Excel sheet is correct)


## Forest plots
### Fig 2: Respiratory compliance (Cdyn)
```{r Cdyn, fig.height=5, fig.width=7, results=FALSE, echo=FALSE}
forest(cdyn.olv, header="Cdyn (OLV)", cex=1.5)
```

### Fig 3: Plateau pressure (Plat)
```{r plateau, fig.height=5, fig.width=7, results=FALSE, echo=FALSE}
forest(plat.tlv, header="Plateau (TLV)", cex=1.5)
forest(plat.olv, header="Plateau (OLV)", cex=1.5)
```

### Fig 4: Peak inspiratory pressure (Peak)
```{r peak, fig.height=6, fig.width=7, results=FALSE, echo=FALSE}
forest(peak.tlv, header="Peak (TLV)", cex=1.5)
forest(peak.olv, header="Peak (OLV)", cex=1.5)
```

### Fig 5: Arterial oxygen pressure (pO2)
```{r arterial, fig.height=6, fig.width=7, results=FALSE, echo=FALSE}
forest(po2.tlv, header="pO2 (TLV)", cex=1.5)

forest(po2.olv, header="pO2 (OLV)", cex=1.5)
```

