---
title: 'Subgroup analysis'
resource_files:
    - ../data
author: "Martin Law"
date: '2022-09-23'
output: html_document
---
---
title: "Subgroup analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library, results="hide", message=FALSE}
library(metafor)
initial.data <- read.csv(file="../data/secondary-outcomes.csv")
head(initial.data)
dat <- escalc(measure="MD", data=initial.data, m1i=m1i, sd1i=sd1i, n1i=n1i, m2i=m2i, sd2i=sd2i, n2i=n2i, slab=study)
```


## Subgroup analysis
Data unclear:

* Multiple/range of values given for tidal volume
* No PEEP values greater than zero (dichotomisation is at zero)
* Li et al. results are split in two in the primary outcome, but not clear if tidal volume etc. are the same in both sets of results.

### Tidal volume (>6 vs <=6mL/kg)
### PEEP (<0 vs 0)
### Anesthesia type (TIVA vs inhaled)
```{r anesthesia}
anes.tiva <- rma(yi, vi, data=dat, subset=(anesthesia=="tiva" & outcome1=="pO2"))
anes.inhaled <- rma(yi, vi, data=dat, subset=(anesthesia=="inhaled" & outcome1=="pO2"))
anes.comp <- data.frame(estimate = c(coef(anes.tiva), coef(anes.inhaled)), stderror = c(anes.tiva$se, anes.inhaled$se),
                       meta = c("tiva","inhaled"), tau2 = round(c(anes.tiva$tau2, anes.inhaled$tau2),3))
rma(estimate, sei=stderror, mods = ~ meta, method="FE", data=anes.comp, digits=3)
```



